\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.52in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\emergencystretch=1em

\newenvironment{tightitemize}
  {\begin{itemize}\setlength{\itemsep}{2pt}\setlength{\parskip}{0pt}\setlength{\parsep}{0pt}\setlength{\topsep}{2pt}}
  {\end{itemize}}

\newenvironment{tightenumerate}
  {\begin{enumerate}\setlength{\itemsep}{2pt}\setlength{\parskip}{0pt}\setlength{\parsep}{0pt}\setlength{\topsep}{2pt}}
  {\end{enumerate}}

\newcommand{\sectiontitle}[1]{%
  {\color{MidnightBlue}\large\bfseries #1\par}%
  {\color{MidnightBlue}\rule{\linewidth}{0.8pt}\par}%
  \vspace{2pt}%
}

\begin{document}
\raggedright

{\fontsize{22}{25}\selectfont\bfseries SIDScore\par}
{\color{Gray}\large One-page repository summary\par}
\vspace{6pt}

\sectiontitle{What It Is}
SIDScore is a Java/ANTLR-based DSL and toolchain for producing Commodore 64 music and sound effects for the SID chip. It lets users write scores, define instruments and tables, audition them in a realtime player, and export C64-ready outputs.

\begin{minipage}[t]{0.49\linewidth}
\sectiontitle{Who It's For}
\textbf{Primary persona:} Commodore 64 composers, retro game/demo developers, and sound designers who want text-based source files for music or SFX plus exportable runtime assets.

\sectiontitle{What It Does}
\begin{tightitemize}
\item Provides a SID-aware DSL with instruments, tables/sequences, reusable imports, and inline \texttt{TUNE} blocks.
\item Parses and validates \texttt{.sidscore} files with ANTLR, then resolves them into timed per-voice score data.
\item Auditions scores with the built-in SRAP realtime player and can optionally use \texttt{vsid} from VICE.
\item Offers a Swing UI with editor, auto-reload, tune selector, oscilloscope views, messages panel, and example browser.
\item Exports \texttt{WAV}, \texttt{ASM}, \texttt{PRG}, and \texttt{SID}; PRG/SID assembly goes through KickAssembler.
\item Builds multi-tune SID bundles from inline tunes, imported subtunes, or CLI \texttt{--stitch} inputs.
\item Supports pluggable export driver backends via Java \texttt{ServiceLoader}; built-in default is \texttt{sidscore}.
\end{tightitemize}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
\sectiontitle{How It Works}
\begin{tightitemize}
\item \textbf{Input:} source files in the SIDScore DSL, plus imported score files and optional waveform tables.
\item \textbf{Front end:} generated \texttt{SIDScoreLexer}/\texttt{SIDScoreParser} parse the source; \texttt{ScoreBuildingListener} resolves imports and builds \texttt{ScoreIR} with metadata, tables, instruments, voices, songs, and subtunes.
\item \textbf{Resolution:} \texttt{SIDScoreIR.Resolver} validates references and transforms \texttt{ScoreIR} into a \texttt{TimedScore}.
\item \textbf{Shared timing path:} \texttt{FrameEventCompiler} converts timed voices into frame events reused by both realtime playback and exported ASM, keeping those paths aligned.
\item \textbf{Playback/export:} \texttt{RealtimeAudioPlayer} and \texttt{RealtimeAudioPlayerUI} render audio or WAV; \texttt{SIDScoreExporter} plus a backend from \texttt{SidDriverRegistry} writes ASM, assembles PRG, and packages PSID/SID output.
\item \textbf{Service layer:} Not found in repo. The codebase shows a local Java CLI/UI toolchain rather than a networked service.
\end{tightitemize}
\end{minipage}

\vspace{4pt}
\sectiontitle{How To Run}
\begin{tightenumerate}
\item Use JDK 21. If needed: \texttt{export JAVA\_HOME=\$(/usr/libexec/java\_home -v 21)}
\item Build: \texttt{mvn -f net.resheim.sidscore/pom.xml -q package}
\item Run the CLI from the repo root:

{\ttfamily\footnotesize
java -cp net.resheim.sidscore/bin/classes:net.resheim.sidscore/lib/antlr-runtime-4.13.1.jar\\
net.resheim.sidscore.SIDScoreCLI examples/test.sidscore\par}

\item Export without realtime audio by adding \texttt{--no-play} and an output flag, for example:

{\ttfamily\footnotesize
java -cp net.resheim.sidscore/bin/classes:net.resheim.sidscore/lib/antlr-runtime-4.13.1.jar\\
net.resheim.sidscore.SIDScoreCLI examples/test.sidscore --sid out.sid --no-play\par}
\end{tightenumerate}

\vfill
{\color{Gray}\footnotesize Repo evidence used: \texttt{README.md}, \texttt{AGENTS.md}, \texttt{net.resheim.sidscore/pom.xml}, and core CLI/IR/export/UI Java sources.}

\end{document}
